### 2019-09-17 NA_paper/manuscript_II/NA_temp/qso_paperII.tex
Update paper and the plots. SAM analysis included.

\newcommand{\lcdm}{$\Lambda$CDM}
\newcommand{\hst}{{\it HST}}
\newcommand{\efr}{$R_{\mathrm{eff}}$}
\newcommand{\galfit}{{\sc Galfit}}
\newcommand{\mbh}{$\mathcal M_{\rm BH}$}
\newcommand{\lhost}{$L_{\rm host}$}
\newcommand{\mr}{Mag$_{\rm ~R}$}
\newcommand{\jcap}{Journal of Cosmology and Astroparticle Physics}
\newcommand{\halpha}{${\it H}\alpha$}
\newcommand{\hbeta}{${\it H}\beta$}
\newcommand{\sersic}{S\'ersic}
\newcommand{\lenstronomy}{{\sc Lenstronomy}}
\newcommand{\reff}{{$R_{\mathrm{eff}}$}}
%\newcommand{\kms}{km~s$^{\rm -1}$}
\newcommand{\kms}{\ifmmode{\,\rm{km}\, \rm{s}^{-1}}\else{$\,$km$\,$s$^{-1}$}\fi}
\newcommand{\sigstar}{{$\sigma_*$}}
\newcommand{\mstar}{{$M_*$}}
\newcommand{\Mgii}{Mg$_{\rm II}$}
\newcommand{\Civ}{C$_{\rm IV}$}
\newcommand{\farcs}{\mbox{\ensuremath{.\!\!^{\prime\prime}}}}% fractional arcsecond symbol: 0.''0
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{abstract}
Supermassive black holes (BH) harbor at the center of galaxies with their masses correlated to the properties of the host galaxies, including absolute magnitude ($Mag$) and stellar mass (\mstar) known as scaling relations (i.e., \mbh-\lhost, \mbh-\mstar). Observational results have indicated evidence that this correlation evolves with cosmic time, suggesting a scenario that the BH growth predates their host. In theory, positive evolution of BH is also predicted by several simulation projects independently. So far, the simulations have reproduced the relations which have a good agreement to the observational sample from local to intermediate redshift ($0.3<z<1$). It is crucial to extend this study to higher redshift ($z>1$), where the predicted relations are more sensitive to the initial simulating assumptions and any inconsistency could help to pinpoint the incorrect ones.
To this end, we use a sample of 32 X-ray-selected broad-line (type-1) AGNs at $1.2 < z < 1.7$ ($\sim 8.5-10$ billion years ago) to make a direct comparison to the predicted sample from two independent state-of-the-art simulating projects, including MassiveBlack-II (MBII) and semi-analytic models (SAMs). We use \hst\ observed images to study the 32 AGNs in multi-bands and deriving the trustworthy stellar mass measurements and the reliable broad \halpha\ emission lines to estimate the \mbh. Taking the selection bias into account, %by adopting the same selection function to choose the simulating sample,
we find that both models agree well with the data, even though they use very different recipes. These agreements indicate the existence of a causal connection between BH and the host galaxy, which could not be explained by purely a stochastic process. To some extent, our result attests that this connection induces an ordering so that the more massive black holes are linked to the more massive masses. Moreover, we find the intrinsic scatter of our high-$z$ sample is not larger than the simulations and local ones, which is against the central limit theorem.

@@

%\section{Introduction}
The discovery of the correlations between the masses (\mbh) of supermassive black holes (SMBH) and the properties of their host galaxies, such as absolute magnitude ($Mag$) and stellar mass (\mstar), indicates that the growth of BH could be connected to its host galaxy formation. So far, the origin that drives this connection is still unknown, due to the daunting range of scales between the dynamical sphere ($\sim$pc) of the SMBH and their host galaxy ($\sim$10 kpc). A dominant interpretation is so-called AGN feedback, assuming that a small fraction of AGN energy injects to their surrounding gas that regulates the growth of SMBH and its host galaxy. In this scenario, the activity of AGN accretion heats and unbinds significant fractions of the gas and inhibits star formation. Some models have been proposed that the connection between SMBH and its host are connected not in a direct manner but assuming that they share a common gas supply~\cite{Cen2015, Menci2016}. On the other hand, without any physical mechanisms, the statistical convergence from galaxy assembly alone (i.e., dry mergers) may reproduce the observed correlations. In this central limit theorem, a stochastic cloud at high-$z$ (higher scatter) would end up with the scaling relations (lower scatter) as observed today.

To understand this connection, the recent works~\cite{Park15, Tre++07, Bennert11, Woo++08} have analyzed the scaling relations beyond the local redshift {($0.3<z<1$)} with active galactic nuclei (AGN) using {\it Hubble Space Telescope} ({\it HST}) and found an evolution that the growth of SMBHs predated to their host galaxies. However, the observational evidence of evolution at high-$z$ is under debated as it relies on our understanding of systematic uncertainties and selection effects. It has been realized that the improper way to consider the uncertainties and selection effects could result in an {\it apparent} evolution and result in an overestimate of the evolution\cite{Volonteri2011}.

%Why comparison between data and model.
%Summary of recently works.
%The reason to extend to high redshift.
Simulating models are the effective tools that help to understand this connection and rule out the assumptions which could not be satisfied with the observations. In the simulating test, the systematic uncertainties and selection bias would be easy to account for. Recent simulating studies by several projects have made predictions which is in good agreement with the analysis by the observations at intermediate redshift range. For example, the state-of-the-art cosmological hydrodynamical simulations of structure formation (MassiveBlackII) have compared the predicted scaling relations to the \hst\ observation at $0.3<z<1$ and predict a positive evolution that SMBH growth predates the host galaxy~\cite{DeG++15}. Several others works have investigated the scaling relations using large-volume simulations, also well matching the local relation with some redshift evolution, including approaches using the Magneticum Pathfinder SPH Simulations~\cite{Steinborn2015}, the Evolution and Assembly of GaLaxies and their Environments (EAGLE) suite of SPH simulations~\cite{Schaye2015}, and Illustris moving mesh simulation\cite{Sijacki2015, Vogelsberger2014}. Besides hydrodynamic simulations, semi-analytic models~\cite{Menci2014, Menci2016} also have made remarkable progress and recovered the local scaling relations~\cite{Kormendy13}. However, to date, the comparisons to the high-resolution (i.e., \hst) sample were still limited at $z<1$ due to the limitation of the observations.

%A good way to understand this connection is to rely on active galactic nuclei (AGN) and trace the scaling relations to higher redshifts, witnessing how and when does it happen. More recently, there is increasing observational evidence indicating the positive offset exist in the correlation at intermediate redshift range ($0.3<z<1$), implying that galaxies built up around the massive potential wells of mature BHs. Stimulated by the observations, theoretical efforts have been made to include the growth of \mbh\ in the framework of cosmological galaxy formation simulations, and generated the predictions of local scaling relations which match the observations well. Moreover, the simulations predict that the positive offset could be even stronger at redshift range $1<z<2$.

%Using the samples predicted by the simulation to compare to the observations is beneficial, in particular at high redshift. First, it helps to directly verify the validity of the initial physics prescriptions adopted in the simulation process, and point out the direction where to improve if needed. Second, in turn, the lessons learned in the simulations could be used to investigate the mechanism of the origin of the scaling relation. For example, the feedback originating in the surroundings of BHs, the major merging activities, and the growth of the \mbh\ and the stellar components as connected to the common gas supply have been invoked as the process leading to the co-evolution. Extending the comparison to high redshift help to explore the origin of the evolution directly. Furthermore, adopting the same selection function enable the particular comparison between two equivalent sample, so as to get rid of the systematic bias lead by the selection effects.

% The work that we want to do
	%Sample selection
	%The advantage of our measurements
	%Compare to which simulation? (some introduction)
	%Any expectation?
	%mention the scatter.
To extend, we collected a sample of 32 \hst-observed AGN systems at redshift range $1.2<z<1.7$ from X-ray coverage fields, including COSMOS~\cite{Civano2016}, (E)-CDFS-S~\cite{Lehmer2005, Xue2011}, and SXDS~\cite{Ueda2008}, to compare to the simulating models. The redshift range of our targets is chosen to be high enough ($z>1$) to detect the existence of the evolution offsets and make the comparison to the models, while low enough ($z<2$) to limit the effect of surface brightness dimming. We selected our AGN sample in a well-defined window as in Figure~\ref{fig:AGN_select}, based on the \mbh\ and Eddington ratio. As shown, the \mbh\ are well below the knee of the BH mass distribution to avoid strong selection bias and the Eddington ratio are above the 1\% level to ensure the homogeneity.

@@

\begin{figure}[t]
\includegraphics[width=0.9\linewidth]{AGN_selection.pdf}
\caption{The selection for the 32 AGN sample. The top and right panels are the BH mass function and Eddington ratio function.
}
\label{fig:AGN_select}
\end{figure}

To make the comparison to the simulating models, we adopt two independent simulating projects, including MassiveBlack-II (MBII) and semi-analytic models (SAM). These two models are based on independent model strategies, i.e., hydrodynamic simulation for MBII and semi-analytic model for SAM, respectively. The MassiveBlack-II (MBII) simulation is the highest resolution at the size of a comoving volume $V_{\rm box} = (100~{\rm Mpc}~h^{-1})$, including a self-consistent model for star formation, black hole accretion, and associated feedback. The large simulation volume enables the simulating objects to evolve independently; the high enough mass and spatial resolution meet the requirements for the object details. On the theoretical side, aimed, high-resolution N-body simulations can study specific galaxy systems. However, understanding the mechanism of the scaling relation requires an analytical description of such processes to be implemented into existing semi-analytic models, such as (SAM). 
MBII and SAM have made successful predictions in previous works \cite{Menci2014, Menci2016, Khandai2015}. We refer the interested readers to these works for more details.

%\section*{Results}
%Selection effect into account
We select the AGNs in the MBII simulation at $z=1.5$ and collect their scaling relations to compare with the observed ones. To take the measurement uncertainty and the selection effect into account, we added the random noise to the simulated sample to mimic the scatter effect. The assumed uncertainties are $\Delta$\mbh =0.4~dex, $\Delta$\mr=0.3~dex, $\Delta$\mstar=0.17~dex and $\Delta L_{\rm bol}$=0.03~dex, respectively, which is comparable to the measurement. We then select the sample that falls in the selection window, as shown in Figure~\ref{fig:selectfunc}. We investigated the predicted relations of the \mbh-\mr\ and \mbh-\mstar\ by the MBII and compared to the observational constraints. In Figure~\ref{fig:MBII_comp}, we show the comparisons of both relations and find that the predicted scaling relations have an excellent agreement to the observations. We carry out the linear fitting of the observed sample and the {\it selection-effect-considered} sample using the same slope value. The mismatch of the interceptions between the two lines are relatively small within $1-\sigma$ level. We adopt the {\sc Linmix} to estimate the intrinsic scatter for both sample. Interestingly, the observed sample have an intrinsic scatter of $0.13\pm0.10$~dex, which is not larger than the one in the MBII, which is $0.23\pm0.06$~dex.

@@

The comparisons between the observed scaling relations to the SAM model are presented in Figure~\ref{fig:SAM_comp}. Rather than predict each individual simulated sample, the SAM model describes the possibility clouds to demonstrate the density distribution of the scaling relations. We use two sets of color contours to demonstrate the possibility distribution at $z=1.5$ epoch, before and after adopting the selection window. The comparisons show great consistency that the hot zones in the SAM {\it selection-effect-considered} contours at $\log($\mbh$)~\in[7.5, 8.56]$ are well matched to the observed relations. We do not estimate the scatter for SAM model, but visually see that the observed relations are mostly located on top of the hot cloud, showing that the observed scatter should not be larger than the model one.

\begin{figure*}[t]%[!b]
\begin{tabular}{c c}
\includegraphics[trim = 0mm 0mm 26mm 0mm, clip, width=0.45\linewidth]{SAM_ML.pdf} &
\includegraphics[trim = 24mm 0mm 0mm 0mm, clip, width=0.45\linewidth]{SAM_MMstar.pdf} \\
\end{tabular}
\caption{ Similar to the Figure~\ref{fig:MBII_comp}, we compare the observation to the SAM models. The blue background contours show the overall sample distribution and the red ones are the relations after considering the selecting effect. We see that the yellow contours are well matched to the hot zones for the red contours.
}
\label{fig:SAM_comp}
\end{figure*}

To help understand if any unexpected selection effects exist, we compare the distribution of the host-total flux ratio among these three samples. For the observed sample, we calculate the flux ratio at the imaging band, i.e., \hst/WFC3. For the simulated sample, we consider the AGN bolometric correction~\cite{Elvis1994} to estimate the AGN light flux at WFC3/F125W band. We compare their host-total flux histogram distribution in Figure~\ref{fig:comp_hist} and see that the three samples are well matched each other. The median values for the flux ratio distribution of the observed, MBII, SAM sample are $37.3\%$, $32.3\%$, and $42.8\%$, respectively. We perform the Kolmogorov-Smirnov test the inferred p-values are 0.34 (for observed -- MBII) and 0.14 (for observed -- SAM), respectively. {\bf Xuheng: more interpretations needs to put here}.

@@

Limited by the observations and the fact they are in good agreements to MBII and SAM, one can not rule out one simulating model from the other. Of course, there are differences between two simulating models. For example, the SAM sample trends to have more scatter than the MBII, especially before applying any selection function. More scatter could arise in SAM because the black hole feeding in this model is merger driven and so there is more stochasticities. In particular, the SAM cloud extends to the high \mbh\ with low stellar mass, which may not exist. These objects are usually with low Eddington ratio; thus an extension of this study to this region would be useful to discriminate between models.

@@

\textbf{Simulations.} 
Describe the approaches used in the simulation.

>>>>

\newcommand{\lcdm}{$\Lambda$CDM}
\newcommand{\hst}{{\it HST}}
\newcommand{\efr}{$R_{\mathrm{eff}}$}
\newcommand{\galfit}{{\sc Galfit}}
\newcommand{\mbh}{$\mathcal M_{\rm BH}$}
\newcommand{\lhost}{$L_{\rm host}$}
\newcommand{\mr}{$Mag_{\rm ~R}$}
\newcommand{\jcap}{Journal of Cosmology and Astroparticle Physics}
\newcommand{\halpha}{${\it H}\alpha$}
\newcommand{\hbeta}{${\it H}\beta$}
\newcommand{\sersic}{S\'ersic}
\newcommand{\lenstronomy}{{\sc Lenstronomy}}
\newcommand{\reff}{{$R_{\mathrm{eff}}$}}
%\newcommand{\kms}{km~s$^{\rm -1}$}
\newcommand{\kms}{\ifmmode{\,\rm{km}\, \rm{s}^{-1}}\else{$\,$km$\,$s$^{-1}$}\fi}
\newcommand{\sigstar}{{$\sigma_*$}}
\newcommand{\mstar}{{$M_*$}}
\newcommand{\Mgii}{Mg$_{\rm II}$}
\newcommand{\Civ}{C$_{\rm IV}$}
\newcommand{\farcs}{\mbox{\ensuremath{.\!\!^{\prime\prime}}}}% fractional arcsecond symbol: 0.''0
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}

@@

\begin{abstract}
Supermassive black holes (BH) harbor at the center of galaxies with their masses (\mbh) correlated to the properties of the host galaxies, including absolute magnitude ($Mag$) and stellar mass (\mstar) known as scaling relations (i.e., \mbh-\lhost, \mbh-\mstar). 
 %Observational results have indicated evidence that this correlation evolves with cosmic time, suggesting a scenario that the BH growth predates their host. In theory, positive evolution of BH is also predicted by several simulation projects independently.
So far, the simulations have reproduced the relations which have a good agreement to the observational sample from local to intermediate redshift ($z<1$). It is crucial to extend this study to higher redshift ($z>1$), where the predicted relations are more sensitive to the initial assumptions and any inconsistency would help to pinpoint the incorrect ones.
To this end, we use a sample of 32 X-ray-selected broad-line (type-1) AGNs at $1.2 < z < 1.7$ ($\sim 8.5-10$ billion years ago) to make a direct comparison to the predicted sample by two independent state-of-the-art simulation projects: MassiveBlack-II (MBII) and semi-analytic models (SAMs). We adopt \hst\ to take images of the 32 AGNs in multi-bands and deriving the trustworthy stellar mass and use the reliable broad \halpha\ emission lines by Subaru/FMOS to estimate the \mbh. Taking the measurement uncertainty and selection bias into account, %by adopting the same selection function to choose the simulating sample,
we find that both models agree well with the data, in terms of the central distribution and scatters. Considering the two models use very different recipes, their agreements to the data indicate the existence of a causal connection between BH and the host galaxy, which could not be explained by purely a stochastic process. The intrinsic scatter of our high-$z$ sample is close to simulations and local ones, which is against the central limit theorem. To some extend, our result attests that there is a physical connection induces an ordering so that the more massive black holes are linked to the more massive masses.

@@

%\section{Introduction}
The discovery of the correlations between the masses (\mbh) of supermassive black holes (SMBH) and the properties of their host galaxies, such as absolute magnitude ($Mag$) and stellar mass (\mstar), indicates that the growth of SMBH could be connected to its host galaxy formation. So far, the origin that drives this connection is still unknown, due to the daunting range of scales between the dynamical sphere ($\sim$pc) of the SMBH and their host galaxy ($\sim$10 kpc). A dominant interpretation is so-called AGN feedback, assuming that a small fraction of AGN energy injects to their surrounding gas that regulates the growth of SMBH and its host galaxy. In this scenario, the activity of AGN accretion heats and unbinds significant fractions of the gas and inhibits star formation. In addition, there are other models have been proposed that the connection between SMBH and their hosts are connected not in a direct manner but assuming that they share a common gas supply~\cite{Cen2015, Menci2016}. Furthermore, without any physical mechanisms, it has been proposed that the statistical convergence from galaxy assembly alone (i.e., dry mergers) may reproduce the observed correlations [ref]. In this central limit theorem, a stochastic cloud at high-$z$ (higher scatter) would end up with the scaling relations (lower scatter) as observed today.

To understand this connection, the recent works~\cite{Park15, Tre++07, Bennert11, Woo++08} have analyzed the scaling relations to intermediate redshift {($0.3<z<1$)} by studying the active galactic nuclei (AGN) using {\it Hubble Space Telescope} ({\it HST}) and found an evolution that the growth of SMBHs predated to their host galaxies. However, the observational evidence of evolution at high-$z$ is under debated as it relies on our understanding of systematic uncertainties and selection effects. It has been realized that the improper way to consider the uncertainties and selection effects could result in an {\it apparent} evolution and result in an overestimate of the evolution\cite{Volonteri2011}.

%Why comparison between data and model.
%Summary of recently works.
%The reason to extend to high redshift.
Simulation models are effective to help understand this connection and rule out the theories/assumptions which could not be verified by the observations. In the simulation test, the systematic uncertainties and selection bias would be easy to account for. Recent studies by several simulation projects have made predictions which is in good agreement with the analysis by the observations at intermediate redshift range. For example, the state-of-the-art cosmological hydrodynamical simulations of structure formation (MassiveBlackII) have compared the predicted scaling relations to the \hst\ observation at $0.3<z<1$ and predict a positive evolution that SMBH growth predates the host galaxy~\cite{DeG++15}. Several others works have investigated the scaling relations using large-volume simulations, resulting in well matches to the local relation with some redshift evolution, including approaches using the Magneticum Pathfinder SPH Simulations~\cite{Steinborn2015}, the Evolution and Assembly of GaLaxies and their Environments (EAGLE) suite of SPH simulations~\cite{Schaye2015}, and Illustris moving mesh simulation\cite{Sijacki2015, Vogelsberger2014}. Besides hydrodynamic simulations, semi-analytic models~\cite{Menci2014, Menci2016} also have made remarkable progress and recovered the local scaling relations~\cite{Kormendy13}. However, to date, the comparisons to the scaling relations by high-resolution sample (i.e., imaged by \hst) are still limited at $z<1$ due to the limitation of the observations.

% The work that we want to do
	%Sample selection
	%The advantage of our measurements
	%Compare to which simulation? (some introduction)
	%Any expectation?
	%mention the scatter.
To extend the comparison to the simulation models to higher redshift, we collected a sample of 32 \hst-observed AGN systems at redshift range $1.2<z<1.7$ from three X-ray coverage fields, including COSMOS~\cite{Civano2016}, (E)-CDFS-S~\cite{Lehmer2005, Xue2011}, and SXDS~\cite{Ueda2008}. The redshift range of our targets is chosen to be high enough ($z>1$) to detect the existence of the evolution offsets and make the comparison to the models, while low enough ($z<2$) to limit the effect of surface brightness dimming. We selected our AGN sample in a well-defined window as in Figure~\ref{fig:AGN_select}, based on the \mbh\ and Eddington ratio \ding{Do we plot figure1 again, or cite to the QSO I paper?}. As shown, the \mbh\ are well below the knee of the BH mass distribution to avoid strong selection bias and the Eddington ratio are mostly above the 0.1 to ensure the homogeneity.

@@

\begin{figure}[t]
\includegraphics[width=0.9\linewidth]{AGN_selection.pdf}
\caption{The selection for the 32 AGN sample. The top and right panels are the BH mass function and Eddington ratio function. \ding{More descriptions to put here.}
}
\label{fig:AGN_select}
\end{figure}

To make the comparison, we adopt two independent simulation projects, including MassiveBlack-II (MBII) and semi-analytic models (SAM). These two models are based on independent model strategies, i.e., hydrodynamic simulation for MBII and semi-analytic model for SAM, respectively. The MassiveBlack-II (MBII) simulation is the highest resolution at the size of a comoving volume $V_{\rm box} = (100~{\rm Mpc}~h^{-1})$, including a self-consistent model for star formation, black hole accretion, and associated feedback. The large simulation volume enables the simulating objects to evolve independently; the high enough mass and spatial resolution meet the requirements for the object details. On the theoretical side, aimed, high-resolution N-body simulations can study specific galaxy systems. However, understanding the mechanism of the scaling relation requires an analytical description of such processes to be implemented into existing semi-analytic models, such as (SAM). 
MBII and SAM have made successful predictions in previous works \cite{Menci2014, Menci2016, Khandai2015}. We refer the interested readers to these works for more details.

%\section*{Results}
%Selection effect into account
We collect a sample of AGNs in the MBII simulation at $z=1.5$ and compare their scaling relations the observed ones. To take the measurement uncertainty and the selection effect into account, we inject the {\it random} noise to the simulated sample to mimic the scattering effect that caused by the uncertainty. The assumed uncertainty levels are comparable to the realistic, which are $\Delta$\mbh =0.4~dex, $\Delta$\mr=0.3~dex, $\Delta$\mstar=0.17~dex and $\Delta L_{\rm bol}$=0.03~dex, respectively. We then select the sample that falls into the selection window, as shown in Figure~\ref{fig:selectfunc}. We investigated the predicted scaling relations by the MBII, including \mbh-\mr\ and \mbh-\mstar, and compared them to the observational constraints, as shown in Figure~\ref{fig:MBII_comp}. From a quick glimpse, one can see that the samples are overlapped with each other, showing an agreement between the predicted scaling relations and observations. To quantify this agreement, we perform the linear fitting to the simulated relations and estimate the best-fit and 1$-\sigma$ confidence interval. We then use the same slope value to obtain the best-fit result for the observed sample. We find that for the \mbh-\mr\ relation, the linear fitting results are almost identical ($0.06$~dex mismatch). For the \mbh-\mstar relations, the mismatch ($0.15$~dex) is small and within 1$-\sigma$ level. We compare how the sample scatter to its central line and find that the simulations and the observations demonstrate a significant similarity. Given that the simulated samples have the same uncertainty and the selection effect, we expect the intrinsic scatter of the scaling relations to be at the same level, which it $0.25$~dex (see method section for details).

@@

The comparisons between the observed scaling relations to the SAM model are presented in Figure~\ref{fig:SAM_comp}. Rather than predict each individual simulated sample, the SAM model describes the possibility clouds to demonstrate the density distribution of the scaling relations. We use two sets of color contours to demonstrate the possibility distribution at $z=1.5$ epoch, before and after adopting the selection window. The comparisons show great consistency that the hot zones in the SAM {\it selection-effect-considered} contours at $\log($\mbh$)~\in[7.5, 8.56]$ are well matched to the observed relations. We do not estimate the scatter for SAM model, but visually see that the observed relations are mostly located on top of the hot cloud, showing that the observed scatter should not be larger than the model one. \ding{To be updated with Nicola's data.}

\begin{figure*}[t]%[!b]
\begin{tabular}{c c}
\includegraphics[trim = 0mm 0mm 24mm 0mm, clip, width=0.45\linewidth]{SAM_ML.pdf} &
\includegraphics[trim = 30.5mm 0mm 0mm 0mm, clip, width=0.45\linewidth]{SAM_MMstar.pdf} \\
\end{tabular}
\caption{ Similar to the Figure~\ref{fig:MBII_comp}, we compare the observation to the SAM models. The blue background contours show the overall sample distribution and the red ones are the relations after considering the selecting effect. We see that the yellow contours are well matched to the hot zones for the red contours.
}
\label{fig:SAM_comp}
\end{figure*}

To help understand if any unexpected selection effects exist, we compare the distribution of the host-total flux ratio among these three samples. For the observed sample, we calculate the flux ratio at the imaging band, i.e., \hst/WFC3. For the simulated sample, we consider the AGN bolometric correction~\cite{Elvis1994} to estimate the AGN light flux at WFC3/F125W band. We compare their host-total flux histogram distribution in Figure~\ref{fig:comp_hist} and see that the three samples are well matched each other. The median values for the flux ratio distribution of the observed, MBII, SAM sample are $37.3\%$, $32.3\%$, and $42.8\%$, respectively. We perform the Kolmogorov-Smirnov (KS) test the inferred p-values are 0.34 (for observed -- MBII) and 0.14 (for observed -- SAM), respectively. \ding{more interpretations needs to put here}.

@@

Limited by the observations and the fact they are in good agreements to MBII and SAM, one can not rule out one simulation model from the other. Of course, there are differences between two simulation models. For example, the SAM sample trends to have more scatter than the MBII, especially before applying any selection function. More scatter could arise in SAM because the black hole feeding in this model is merger driven and so there is more stochasticities. In particular, the SAM cloud extends to the high \mbh\ with low stellar mass, which may not exist. These objects are usually with low Eddington ratio; thus an extension of this study to this region would be useful to discriminate between models.

@@

%\textbf{Simulations.} 
%Describe the approaches used in the simulation.

\textbf{Linear fitting and scatter comparison}.  
%How the fitting is done. The comparing of the histogram and the KS test. The scatter. Figures.
To quantitatively understand the consistency between the simulated scaling relations and the observing ones, we use linear fittings and compare their result. Since our selection window has hard cut on the \mbh\ value and the scatter on the host galaxies' properties are larger, we thus fit the host's properties as a function of \mbh. We adopt the {\sc Scipy} package to estimate the best-fit line and its 1-sigma region for the simulated sample. We use the sample slope value to fit for the observations. The comparing results are showing in Figure~\ref{fig:MBII_comp}. To estimate the scatter of the sample, we plot the histogram of the offset value of the sample that deviated from their best-fit. For MBII model, the result are shown in Figure~\ref{fig:offset_comp}. We perform the KS test between the simulation sample and observation sample, and find the p-value are $\sim0.3$ for both \mbh-\mr\ and \mbh-\mstar\ relations. Considering that the compared simulation sample have the same uncertainty level with same selection effect, we expect they have the same intrinsic scatter level. We adopt {\sc Linmux} to estimate the intrinsic scatter from the overall sample and obtain its value value is $0.25$~dex.

\begin{figure*}[t]%[!b]
\begin{tabular}{c c}
\includegraphics[width=0.45\linewidth]{comp_scatter_ML.pdf} &
\includegraphics[width=0.45\linewidth]{comp_scatter_MM.pdf} \\
\end{tabular}
\caption{The histogram comparison of the scatter of the sample offset to its best-fit relation. The standard derivations are identically equal to $0.3$~dex for both HST sample and MBII sample on both sides.
}
\label{fig:offset_comp}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
